Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-16 manuscript/manuscript.Rmd
Geomorph LM seems broken

```{r geomorph_lm, cache=TRUE}
fmted <- format_for_gpagen(no_st)
allsplit <- str_split_fixed(dimnames(fmted)$id, "_", 3)
family_vec <- allsplit[, 1]
role_vec <- allsplit[, 2]
ind_vec <- allsplit[, 3]
gpaed <- gpagen(fmted, ShowPlot=F)

@@

advanced.procD.lm(gpaed$coords ~ ind_vec,  ~ role_vec * ind_vec, ~ family_vec, iter=499)
```

>>>>

<!--
```{r geomorph_lm, cache=TRUE}
fmted <- format_for_gpagen(no_st)
allsplit <- str_split_fixed(dimnames(fmted)$id, "_", 3)
family_vec <- allsplit[, 1]
role_vec <- allsplit[, 2]
ind_vec <- allsplit[, 3]
gpaed <- gpagen(fmted, ShowPlot=F)

@@

advanced.procD.lm(gpaed$coords ~ ind_vec,  ~ role_vec * ind_vec, ~ family_vec, iter=499)
```
-->
